Thesis Title

### 2022-05-28 chapters/chapter_5.tex
Updates from Overleaf

\begin{figure*}[h!]
\centering
\includegraphics[width=\textwidth]{figures/chapter 5/Supplemental Figure 1.png}
\caption{LMAS misassembly classification. Misassembled contigs are classified into 6 main categories: chimera, insertion, deletion, inversion, rearrangement, translocation and duplication, according to the mapping orientation, the distance between blocks in the contig and the mapping coordinates in the reference replicon. If a contig is classified as being chimeric, no further classification is performed. The other categories are classified independently of each other, with combinations being possible, to better reflect the differences in comparison to the reference. If a contig is broken into multiple sequence blocks but fails to be classified in any of the previous categories, it is reported as being inconsistent}
\label{fig:chap5_sup_figure_1}
\end{figure*}

>>>>

\begin{figure*}[]
\centering
\includegraphics[scale=0.95]{figures/chapter 5/Supplemental Figure 1.png}
\caption{LMAS misassembly classification. Misassembled contigs are classified into 6 main categories: chimera, insertion, deletion, inversion, rearrangement, translocation and duplication, according to the mapping orientation, the distance between blocks in the contig and the mapping coordinates in the reference replicon. If a contig is classified as being chimeric, no further classification is performed. The other categories are classified independently of each other, with combinations being possible, to better reflect the differences in comparison to the reference. If a contig is broken into multiple sequence blocks but fails to be classified in any of the previous categories, it is reported as being inconsistent}
\label{fig:chap5_sup_figure_1}
\end{figure*}

\section{Per Reference Metrics}

\subsection{General contig information}

\begin{itemize}
    \item \textbf{Contigs:} The total number of contigs in the assembly that align to the reference replicon;
    \item \textbf{Basepairs:} The total number of bases in the assembly that align to the reference replicon;
    \item \textbf{Number of ‘N’s:} Number of uncalled bases (N's) in the contigs that align to the reference replicon.
\end{itemize}
